\LARGE \bf Generalizing Informed Sampling for Asymptotically Optimal Sampling-based Kinodynamic Planning via Markov Chain Monte Carlo

### 2017-09-16 paper.tex
tiny fix

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_1}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_2}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_3}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_4}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
		\caption{\captionstyle Problem 1 : 3DOF planar arm move from a start to a goal while starting and ending with zero velocities.}
		\vspace{6pt}
		\label{fig:planning_efficiency:3dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_1}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_2}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_3}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_4}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
		\caption{\captionstyle Problem 2 : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
		\vspace{6pt}
		\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_1}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_2}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_3}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_4}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
	\caption{Problem 3 : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
	\label{fig:planning_efficiency:herb:example}
	\end{subfigure}
	\caption{\captionstyle Three problems are used to evaluate planning efficiency.
	These problems are defined in state spaces with different dimensions and different kinodynamics.}
	\label{fig:problems}
\end{figure*}

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
		\caption{\captionstyle Problem 1 - 6 Dimensions.}
		\label{fig:planning_efficiency:3dof:general}
	\end{subfigure}	
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
		\caption{\captionstyle Problem 2 - 12 Dimensions.}
		\label{fig:planning_efficiency:6dof:hammering}
	\end{subfigure}
	\begin{subfigure}[b]{0.325\textwidth}
	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
	\caption{\captionstyle Problem 3 - 14 Dimensions.}
	\label{fig:planning_efficiency:herb:batting}
    \end{subfigure}
	\caption{\captionstyle Planning Efficiency of four different samplers (RS, HRS, MH and HNR) in three problems. 
	The X axis is the planning time. 
	The Y axis is the ration of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
	\label{fig:planning_efficiency}
\end{figure*}

>>>>

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_1}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_2}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_3}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_4}
		\includegraphics[height=2.45cm]{fig/planning_efficiency/3dof_5}
		\caption{\captionstyle Problem 1 : 3DOF planar arm move from a start to a goal while starting and ending with zero velocities.}
		\vspace{6pt}
		\label{fig:planning_efficiency:3dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
	    \centering
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_1}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_2}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_3}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_4}
		\includegraphics[height=3cm]{fig/planning_efficiency/6dof_5}
		\caption{\captionstyle Problem 2 : 6DOF snake hammers the end-effector into the wall while starting with zero velocity.}
		\vspace{6pt}
		\label{fig:planning_efficiency:6dof:example}
	\end{subfigure}
	\begin{subfigure}[b]{\textwidth}
    \centering
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_1}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_2}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_3}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_4}
    \includegraphics[height=2.7cm]{fig/planning_efficiency/herb_batting_5}
	\caption{Problem 3 : HERB sweeps a cup on a table, in which the right arm starts with zero velocity and ends with non-zero velocity.}
	\label{fig:planning_efficiency:herb:example}
	\end{subfigure}
	\caption{\captionstyle Three problems are used to evaluate planning efficiency.
	These problems are defined in state spaces of different dimensions and subject to different kinodynamics.}
	\label{fig:problems}
\end{figure*}

\begin{figure*}[t!]
	\centering
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/3dof_general}
		\caption{\captionstyle Problem 1 - 6 Dimensions.}
		\label{fig:planning_efficiency:3dof:general}
	\end{subfigure}	
	\begin{subfigure}[b]{0.325\textwidth}
		\includegraphics[width=\linewidth]{fig/planning_efficiency/6dof_hammering}
		\caption{\captionstyle Problem 2 - 12 Dimensions.}
		\label{fig:planning_efficiency:6dof:hammering}
	\end{subfigure}
	\begin{subfigure}[b]{0.325\textwidth}
	\includegraphics[width=\linewidth]{fig/planning_efficiency/herb_batting_efficiency}
	\caption{\captionstyle Problem 3 - 14 Dimensions.}
	\label{fig:planning_efficiency:herb:batting}
    \end{subfigure}
	\caption{\captionstyle Planning Efficiency of four different samplers (RS, HRS, MH and HNR) in three problems. 
	The X axis is the planning time. 
	The Y axis is the ratio of the current best and the optimal $ \cbest / c^*_{\rm best} $.}
	\label{fig:planning_efficiency}
\end{figure*}
